One-Step, Three-Factor Authentication in a Single Earpiece

### 2017-04-05 paper.tex
minor fixes

\begin{table*}[h]
\centering
\begin{tabularx}{.85\textwidth}{lrrrrrrrrrr}
& \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P7}}\\
\textbf{Task} & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR\\ \hline
Breathe & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0\\
Breathe - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0.0253 & 0 & 0\\
Face & 0.0002 & 0.0253 & 0.0005 & 0.0253 & 0 & 0.0127 & 0 & 0 & 0 & 0\\
Listen & 0 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Sequence & 0 & 0.0506 & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0.0007 & 0.0127\\
Song	 & 0.0002 & 0.0380 & 0 & 0 & 0	 & 0 & 0 & 0.0127 & 0.0007 & 0.0127\\
Song - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127\\
Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\
\textbf{Best Task} & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\ \hline
\end{tabularx}
\caption{FAR and FRR performance of each task for each participant using data from the left ear. P4 and P6 achieve perfect zero FARs and FRRs across all tasks and so are not shown here.}
\label{tab:farfrrall}
\end{table*}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lrr}
 \textbf{Training Scheme} & \textbf{FAR} & \textbf{FRR}\\
\hline
Between-participants, any task & 0.000074 & 0.004424\\
Between-participants, same task & 0.000724 & 0.001522\\
\hline
Within-participants & 0.002523 & 0.039702\\
\hline
\end{tabular}
\end{center}
\caption{Mean FAR and FRR for all participants and passthoughts across three different training schemes.}
\label{tab:compare}
\end{table}

@@

Among our authentication training schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial. The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants. Classifiers overall distinguished the \textit{breathe} and \textit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e. that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \textit{song}. We were able to achieve these results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes). This short timespan is somewhat surprising, given that tasks like \textit{song} presumably change over longer time periods.

@@

\section{Acknowledgments}

@@

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
%\balance

>>>>

\begin{table*}[h]
\centering
\begin{tabularx}{.85\textwidth}{lrrrrrrrrrr}
& \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{P2}} & \multicolumn{2}{c}{\textbf{P3}} & \multicolumn{2}{c}{\textbf{P5}} & \multicolumn{2}{c}{\textbf{P7}}\\
\textbf{Task} & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR & FAR & FRR\\ \hline
Breathe & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127 & 0 & 0\\
Breathe - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0.0253 & 0 & 0\\
Face & 0.0002 & 0.0253 & 0.0005 & 0.0253 & 0 & 0.0127 & 0 & 0 & 0 & 0\\
Listen & 0 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Sequence & 0 & 0.0506 & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0.0007 & 0.0127\\
Song	 & 0.0002 & 0.0380 & 0 & 0 & 0	 & 0 & 0 & 0.0127 & 0.0007 & 0.0127\\
Song - open & 0.0002 & 0.0127 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0.0127\\
Speech & 0.0002 & 0 & 0.0005 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.0002 & 0 & 0 & 0 & 0 & 0 & 0 & 0  & 0 & 0.0127\\
\textbf{Best Task} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0} & \textbf{0}\\ \hline
\end{tabularx}
\caption{FAR and FRR performance of each task for each participant using data from the left ear. P4 and P6 achieve perfect zero FARs and FRRs across all tasks and so are not shown here.}
\label{tab:farfrrall}
\end{table*}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lrr}
 \textbf{Analysis Scheme} & \textbf{FAR} & \textbf{FRR}\\
\hline
Between-participants, any task & 0.000074 & 0.004424\\
Between-participants, same task & 0.000724 & 0.001522\\
Within-participants & 0.002523 & 0.039702\\
\hline
\end{tabular}
\end{center}
\caption{Mean FAR and FRR for all participants and passthoughts across three analysis schemes.}
\label{tab:compare}
\end{table}

@@

Among our authentication analysis schemes, the between-participants analyses achieved lower FAR than within-participants, indicating the inherence factor (a person's brainwaves) is likely stronger than the knowledge factor (their choice of task), though the knowledge factor is not trivial. The \textit{breathe}, \textit{breathe-open}, and \textit{listen} tasks performed exceedingly well among participants. Classifiers overall distinguished the \textit{breathe} and \textit{listen} tasks even compared to the same tasks from other participants, implying that these tasks are expressed differently for each participant, i.e. that they have an inherence factor sufficient for authentication, even though they task do not involve an explicit secondary knowledge factor as in \textit{sport} or \textit{song}. We were able to achieve these results by generating feature vectors based on only 500ms (300 voltage readings across the three electrodes). This short timespan is somewhat surprising, given that tasks like \textit{song} presumably change over longer time periods.

@@

\section{Acknowledgments}
Witheld for blind review.

@@

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
% \balance
